Distributional State Aggregation

### 2020-02-24 minutia/paper/paper.tex
paper updated

    \begin{abstract}
        Promising advances in deep reinforcement learning suggests several application to the algorithms.
        However robustness of these algorithms remains doubts to trust these algorithms in practice.
        In this paper we study resistance of the state-of-the-art algorithms to environment dynamics.
        We then show the amount of robustness we can achieve as a guarantee of performance in presence of those changes.
    \end{abstract}

    \section{Introduction}
    Real-world problems embody high-dimensional state spaces where in computational issues
    arise.
    Various approximation methods are proposed in the literature to reduce the resulted value function
    dimensionality \cite{Sutton1998, Francois-Lavet2018}.
    State aggregation is one of the simplest and most analytically transparent state representation approximation.

    Although state aggregation may not generalize as well as neural network-based methods, the techniques has both
    analytical and practical advantages \cite{Lagoudakis2003}.
    In comparison, state aggregation takes less computation power to calculate representative features.
    Moreover, analysis and troubleshooting in a state aggregation process is more obvious than a black-box neural
    network.
    Approximation is a corner stone in all successful RL methods to hold a "good" mapping between a large state
    space to a much smaller one where in value function is computable or at least feasible.
    These "good" approximators can end up with "good" features to represent the projected state space.

@@

    \section{Markov Decision Processes}
    Reinforcement learning problems can be formulated as an Markov decision process (MDP)\cite{Puterman1994}.
    Discrete discounted reward criterion is the center of focus for ease of exposition in this paper.
    For an environment and a decision maker, state space $S$ and action space $A$ are defined, respectively.
    The transition probabilities $T$ describe how likely is the next state $s'$ by taking a specific action $a$ by
    the agent in a certain state $s$ which will receive $r$ as reward.
    For a taken action $a_i$ in the state $s_i$, the decision maker will be ended up in state $s_{i+1}$ by the
    transition probabilities $P : S \times A \times S \rightarrow [0, 1]$ and wil receive reward $r_{i+1}$ from the
    rewards $R : S \times A \rightarrow \mathbb{R}$: \\
    \begin{equation}
        s_{i+1} = T(s_{i+1}|s_i, a_i)
    \end{equation}

>>>>

    \begin{abstract}
        We present a state aggregation algorithm and a learning algorithm based on the former to solve a stochastic
        problem.
        The presented aggregation algorithm uses range of collected samples to provide the proper aggregation
        \textit{buckets}.
        Our approach is a batch learning by which we detect the \textit{splitting policy} using inter-quartile range
        of data for each feature.
        We then show the amount of robustness we can achieve as a guarantee of performance in presence of those
        aggregation policies.
    \end{abstract}

    \section{Introduction}
    Real-world problems embody high-dimensional state spaces where in computational issues
    arise.
    Various approximation methods are proposed in the literature to reduce the resulted value function
    dimensionality\cite{Sutton1998, Francois-Lavet2018}.
    State aggregation is one of the simplest and most analytically transparent state representation approximation.

    Although state aggregation may not generalize as well as neural network-based methods, the techniques has both
    analytical and practical advantages\cite{Lagoudakis2003}.
    In comparison, state aggregation takes less computation power to calculate representative features.
    Moreover, analysis and troubleshooting in a state aggregation process is more obvious than a black-box neural
    network.
    Approximation is a corner stone in all successful RL methods to hold a "good" mapping between a large state
    space to a much smaller one where in value function is computable or at least feasible.
    These "good" approximators can end up with "good" features to represent the projected state space.

@@

    \section{Markov Decision Processes}
    Reinforcement learning problems can be formulated using a Markov Decision Processes (MDP)
    framework\cite{Puterman1994, Bertsekas}.
    MDPs facilitate handling sequential decision-making under uncertainty.
    Discrete discounted reward criterion is the center of focus for ease of exposition in this paper.
    For an environment and a decision maker, state space $S$ and action space $A$ are defined, respectively.
    The transition probabilities $T$ describe how likely is the next state $s'$ by taking a specific action $a$ by
    the agent in a certain state $s$ which will receive $r$ as reward.
    For a taken action $a_i$ in the state $s_i$, the decision maker will be ended up in state $s_{i+1}$ by the
    transition probabilities $P : S \times A \times S \rightarrow [0, 1]$ and wil receive reward $r_{i+1}$ from the
    rewards $R : S \times A \rightarrow \mathbb{R}$: \\
    \begin{equation}
        s_{i+1} = T(s_{i+1}|s_i, a_i)
    \end{equation}
